---
title: "Assignment 3_MSBA_6441_Causal Inference via Econometrics and Experimentation_AT_SM"
author: "Aditya Tomar, Shubham Midha"
output: pdf_document
date: "2022-11-21"
---

## (a)	What is Wrong with Bob’s RoI Calculation? 

Keyword searches include the name of the company.
These people most likely would already be aware of the website and would be
actively looking for it. 

For example: if a consumer used the search term “Bazaar shoes” and clicked 
on the sponsored ad that came up in the results. If the ad weren’t there, 
the consumer would very likely click on organic link and company wouldn't even
have to pay for the click cost for sponsored ads.

Also, it is mentioned in the case that the conversion probability and margin 
per conversion are the same for all consumers, irrespective of how they land
at the website.

Hence for calculating the ROI of the sponsored campaign, we need to find out
how many conversions can truly be attributed to sponsored ads.

## (b) Define the Treatment and Control: 
Platform is the unit of observation as the sponsored ads ran on Google
(goog) for Weeks 1 - 9 and got stopped because of the technical glitch
for Weeks 10 - 12.

Treatment is stopping of sponsored ads post week 9 for Google.

Treatment group: Google - Week 10, 11 & 12
Control groups: Yahoo, Bing, and Ask


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading the data
```{r}
library(dplyr)
library(ggplot2)
library(plm)
library(readr)

# import data
data = read_csv("did_sponsored_ads.csv")
```

### Exploring and checking for number of weeks
```{r}
# Data Exploration

# How many weeks does the data cover? 
# What is the minimum and maximum week in the data? 

min(data$week)
max(data$week)

```
Data is for 12 weeks

### Manipulating Data and adding additional treatment/control columns
```{r}
# Adding sponsored and organic traffic to compute total web traffic
data$total_traffic = data$avg_spons + data$avg_org

# Adding treatment variable - 1 for week 10, week 11, and week 12; 0 for rest
# Only for Google

data = data %>%
  mutate(treatment = ifelse((week>9 & platform=='goog'), 1,0))

# Adding a variable for indicating post period 
data = data %>%
  mutate(post_flag = ifelse((week>9), 1,0))

# Adding a flag for Google
data = data %>%
  mutate(google_flag = ifelse((platform=='goog'), 1,0))
```


## (c)	Consider a First Difference Estimate: 

Simply observing the treated unit (Google) by calculating first  difference
that  is,  the  %  change  in  web  traffic  arriving from Google; 
(after – before) / before
This estimate is the pre-post difference in the treated cohort;

Problem: However, this approach assumes that the first nine weeks were 
systematically similar to the last three weeks

```{r}
google_data = data %>% filter(platform == 'goog')

hist(google_data$total_traffic,breaks=10)

summary(lm(total_traffic ~ treatment, data=google_data))
```

Problem: However, this approach assumes that the first nine weeks were 
systematically similar to the last three weeks
This is not the case as we can see a clear uptrend and hence we should control
for the variation in weeks or try difference in differences method.

Also the p-value for the coefficients is 0.576 which is above our acceptable
threshold of 0.05, hence we cannot interpret the coefficient meaningfully

## (d) Calculate the Difference-in-Differences

```{r}
bing_data = data %>% filter(platform == 'bing')
yahoo_data = data %>% filter(platform == 'yahoo')
ask_data = data %>% filter(platform == 'ask')

# Before running DiD, we need to check for parallel trend assumption in 
# pre-period

ggplot(google_data, aes(x=week, y= total_traffic, color = 'Google')) +
  geom_line() +
  geom_line(aes(x=week, y= total_traffic, color = 'Bing'), data = bing_data) +
  geom_line(aes(x=week, y= total_traffic, color = 'Yahoo'), data = yahoo_data) +
  geom_line(aes(x=week, y= total_traffic, color = 'Ask'), data = ask_data) +
  geom_vline(xintercept = 9,color='black') +
  scale_x_continuous(breaks = seq(1, 12, by = 1)) +
  labs(y = "Total Traffic", x = "Week") +
  theme_classic()
```

```{r}
# Evaluating parallel trends assumption
summary(lm(total_traffic ~ google_flag*factor(week), data=data))
```
Since we observe statistically significant coefficients for a few weeks prior
to week 9, our parallel trends assumptions is violated

```{r}
# Performing the DiD
did <- lm(total_traffic ~ google_flag + post_flag + google_flag * post_flag, data=data)
summary(did)
```

From the results obtained, we can say that due to the technical glitch causing 
the absence of Google sponsored ads, there is a decrease of 9910 clicks 
for the Google platform. 
In terms of statistical significance, the p-value(0.007) is lower than the the
threshold of 0.05, implying that it is statistically significant.

This confirms our hypothesis that there might be few users who would visit the 
website via organic links in the absence of sponsored ads, however we would lose
few customers too.

## (e) Given Your Treatment Effect Estimate, Fix Bob’s RoI Calculation

The ROI calculation that was calculated by Bob had the following metrics:
An average revenue per click of 0.12 x 21, or $2.52, which implies an ROI of
(2.52– 0.60)/(0.60), or 320.0%.

The discussion revolves Bob and Myra where the latter suggests that they can 
save money by showing the ads only to relevant people. The keywords searches
already include names of bazaar.com, which means that users were aware of what
they were searching - which makes them discuss if they even need to show ads to 
the users.

```{r}
# regressing the average organic clicks for the treatment, pre_post
organic <- lm(avg_org ~ google_flag + post_flag + google_flag * post_flag, data=data)
summary(organic)
```
First, out of all the traffic, we first calculate the proportion of true traffic:
By this we mean that we want to find the proportion of clicks truly motivated 
by sponsored ad between it and clicks by customers who would still 
visit Bazaar.com irrespective of sponsored ads.

Looking at our co-efficient we obtained: 
X = 9,910 (clicks truly motivated by sponsored ad)
Y = 2,293.2 (clicks by customers who would still 
visit Bazaar.com irrespective of sponsored ads)

Proportion of true traffic = X/(X+Y) = 9,910/(9,910+2,293) = 0.8120954 (81%)

We know calculate the new return of investment:
```{r}
New_ROI = ((21 * 0.12 * 0.8120954- 0.6)/0.6)*100
New_ROI
```

With respect to the new estimated treatment effect, the new ROI is 241.08%.


Without the wrong expansion of supported promotion income, the recently 
determined return on initial capital investment of 320% is diminished to 241%,
which is as yet a decent profit.
